Linking microbial communities to ecosystem functions: what we can learn from genotype-phenotype mapping in organisms

### 2019-07-02 manuscript/main.tex
Update text

\section*{Tasks} 
\begin{enumerate}
\item What is novel about this? The first anyone has treated an ecosystem like an
organism. The first time anyone has done this correlative approach well
by considering environmental and spatial structure in the data. 
\item Figure out variance partitioning (with Hannah)
\item Maybe variance partitioning plus correlations (varPart)
\item Do PC correction in all combinations
\item Identify significant taxa and build a venn diagram figure (or
something)
\item 
\end{enumerate}
\section{Introduction}

I want to know whether microbial community composition is important for determining ecosystem-scale functions independent of the underlying environmental variation.

Microorganisms mediate many biogeochemical processes, but despite 
much effort to link microbial communities
to these functions the mechanism by which they regulate these
processes remains unknown. Ecologists have investigated the effects of changing
biodiversity on ecosystem function for decades, but many of their approaches
are not applicable in microbial ecology due to the nature of microbial data. 
This limits our ability to predict and manage globally relevant biogeochemical cycles. To
address this challenge, we propose integrating current theory on community
assembly and the functioning of ecosystems with lessons from genotype-phenotype
mapping in quantitative genetics. This will address the
question of how does variation in microbial community structure contribute to
variation in the rate of ecosystem function?

>>>>

\section*{Tasks} 
\begin{enumerate}
\item What is novel about this? The first anyone has treated an ecosystem like an
organism. The first time anyone has done this correlative approach well
by considering environmental and spatial structure in the data. 
\item Interpret model output
\item Decide whether to include Gabon data, Brazil data, or both
\end{enumerate}

\section{Outline}
\begin{enumerate}
  \item First paragraph laying out the problem
  \item BEF research on macroorganisms has demonstrated that productivity increases with
    taxonomic and functional diversity.
  \item This research has been less definitive for microbial communities. There
    are two main hypotheses that aren't very well supported: function should
    scale with community size or abundance of marker genes.
  \item We propose that this BEF approach to linking microbial communities
    to ecosystem function is inappropriate and instead this problem is more
    analagous to the population genetics challenge of linking many genetic
    markers to an organismal phenotype.
  \item To incorporate this idea in to microbial community function research,
    we should consider the 
\end{enumerate}

\section{Introduction}

Microorganisms mediate many biogeochemical processes and yet the link between
microbial biodiversity and ecosystem function remains unknown. 
Ecologists have investigated the effects of changing
biodiversity on ecosystem function for decades. This research has primarily
focused on linking terrestrial plant community richness with productivity
\citep{hooper2005}. More recently, there has been an interest in linking
microbial community composition to host disease, soil greenhouse gas emissions,
and plant productivity. However, it remains unclear the extent to which 
microbial community composition is important for understanding ecosystem-scale
functions.  This uncertainty limits our ability to predict and manage 
globally relevant biogeochemical cycles and host traits. To
address this challenge, we propose integrating current theory on community
assembly and the functioning of ecosystems with lessons from genotype-phenotype
mapping in quantitative genetics. This connection will address
whether microbial community
composition is important for determining ecosystem-scale functions independent
of the underlying environmental variation.
